### 2013-02-14 doc/xps2013/proposal.tex
pass on research section.

We need to rewrite the aggregator to build in a hierarchical virtual network layer.  The first layer of this hierarchy is to treat all processors at a given system node as a single destination. We intend to continue to use the lock-free single-threaded \gasnet~communication layer that we have been using, as we have found the lock-based one to incur too high of an overhead for our purposes.  Thus the aggregator will need to very carefully utilize lock-free data-structures and interact with \gasnet~carefully.
%%Didn't understand Myers suggestion here.

@@

\paragraph{User-level RDMA:} Certain commodity networking hardware today
supports remote direct memory access (RDMA). Unfortunately, \emph{how} it is
implemented is so primitive and low-level that it is difficult or impossible
to efficiently use in practice. We start with a short description of the
current semantics of RDMA implementations. Next we describe the research we
wish to undertake to make RDMA more useful.

@@

%% The second half of this paragraph is really confusing, I have just a minimal clue of what it is talking about. And the little I understand sounds a bit vague and not directly related to grappa.
The second challenge is that the virtual to physical address translation on the cards requires the operating system to pin translations.  This removes paging flexibility from the operating system, because runtime systems are (rationally) built to expect data structures to be in memory capable of RDMA or not.  Those in RDMA memory must be pinned.  In the long run, the solution here likely lies at the intersection of what progress is occurring in processor support for virtual machines and virtual memory translation for I/O.  Our goal will be to study carefully the I/O virtualization proposals put forth by major processor manufactures and devise solutions that enable RDMA to capitalize on these developments.

>>>>

We need to redesign the aggregator to build in a hierarchical virtual network layer.  The first layer of this hierarchy is to treat all processors at a given system node as a single destination. We intend to continue to use the lock-free single-threaded \gasnet~communication layer that we have been using, as we have found the lock-based one to incur too high of an overhead for our purposes.  Thus the aggregator will need to very carefully utilize lock-free data-structures and interact with \gasnet~carefully.
%%Didn't understand Myers suggestion here.

@@

\paragraph{User-level RDMA:} Certain commodity networking hardware today
supports remote direct memory access (RDMA). Unfortunately, \emph{how} it is
implemented is so primitive and low-level that it is difficult or impossible
to efficiently use in practice. Below we start with a short description of the
current semantics of RDMA implementations. Next we describe the research we
wish to undertake to make RDMA more useful.

@@

The second challenge is that the virtual to physical address translation is
necessary for RDMA operations to be meaningful. Current systems require the OS
to pin translations so cards can operate directly on physical addresses. This
removes paging flexibility from the operating system and requires runtime
systems to be aware that this is happening, which limits overall usability.
We will explore recent advances in supporting direct memory access with address translation (e.g., AMD IOMMU) to support flexible RDMA operation that go through full physical address translation without having to interrupt a general-purpose core.

% In the long run, the solution here likely
% lies at the intersection of what progress is occurring in processor support
% for virtual machines and virtual memory translation for I/O. Our goal will
% be to study carefully the I/O virtualization proposals put forth by major
% processor manufactures and devise solutions that enable RDMA to capitalize
% on these developments.
